Efficiently Handling Guards in the low level design of RPython's tracing JIT

### 2012-07-24 talk/vmil2012/paper.tex
add to references to the related work section
a paragraph about self

@@

>>>>

Deutsch et. al.~\cite{XXX} describe the use of stack descriptions
to make it possible to do source-level debugging of JIT-compiled code.
Self uses deoptimization to reach the same goal~\cite{XXX}.
When a function is to be debugged, the optimized code version is left
and one compiled without inlining and other optimizations is entered.
Self uses scope descriptors to describe the frames
that need to be re-created when leaving the optimized code.
The scope descriptors are between 0.45 and 0.76 times
the size of the generated machine code.

@@

\bivab{mention Gal et al.~\cite{Gal:2009ux} trace stitching}
and also mention \bivab{Dynamo's fragment linking~\cite{Bala:2000wv}} in
relation to the low-level guard handling.
